A Pilot Multicenter Cluster Randomized Trial to Compare The Effect of Trauma Life Support Training Programs on Patient and Provider Outcomes

### 2023-08-07 pilot-publication/lab-book.Rmd
Document new error when trying to calculate differences between data.frames

## Strange error when running bootstrap on real data

I get this strange error when I try to run the bootstrap on the real data:

@@

>>>>

## Errors when running bootstrap on real data

1. I first got this strange error when I try to run the bootstrap on the real data:

@@

2. I then got this error:

```{r}
## Error in Ops.data.frame(outcomes.tables$post.training[2:4], outcomes.tables$pre.training[2:4]) : 
##   ‘-’ only defined for equally-sized data frames
## Calls: boot -> statistic -> Ops.data.frame
## Execution halted
```

Will have to look into that.
